Toxic Code Snippets on Stack Overflow

### 2017-11-13 cloverflow-tse/cloverflow.tex
Corrected the numbers from Figure 9.

We asked the remaining 200 participants for the origins of code snippets in
their answers. We provided six locations including the answerer's personal
projects, the answerer's company projects, open source projects, writing the
code from scratch, copying and modifying the code from the question, and others
(e.g.\ code that are copied from other questions or answers on Stack Overflow)
and we asked them to rate how often they copied the code from these locations. The
results are shown in \Cref{fig:survey_snippet_source}. Looking at the Very
Frequently section, we can see that the answerers mainly write new code from
scratch (71) or copy and modify the code snippets from the question for each answer (56),
while fewer numbers are from other sources including their personal projects
(42), their company projects (10), and open source projects (14). Although
copying from open source projects is not the most popular choice, the answerers
still rely on them sometimes. As shown in the figure, there are 14, 31, and 33
participants who frequently, occasionally, and rarely copied code snippets from
open source projects.

>>>>

We asked the remaining 200 participants for the origins of code snippets in
their answers. We provided six locations including the answerer's personal
projects, the answerer's company projects, open source projects, writing the
code from scratch, copying and modifying the code from the question, and others
(e.g.\ code that are copied from other questions or answers on Stack Overflow)
and we asked them to rate how often they copied the code from these locations. The
results are shown in \Cref{fig:survey_snippet_source}. Looking at the Very
Frequently section, we can see that the answerers mainly write new code from
scratch (106) or copy and modify the code snippets from the question for each answer (66),
while fewer numbers are from other sources including their personal projects
(28), their company projects (4), and open source projects (9). Although
copying from open source projects is not the most popular choice, the answerers
still rely on them sometimes. As shown in the figure, there are 14, 31, and 33
participants who frequently, occasionally, and rarely copied code snippets from
open source projects.
